Predicting Tags for StackOverflow Posts

### 2013-03-03 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 3213e7b268d556d9b3d3875735f0ea7e3956a490 [formerly d53aa6d174d1a5acbeb2c9cec4b7209d40fab881]
Former-commit-id: 0bf54a4eb3a6bc0357fd06bfd13d6cce3fd6379a

\begin{abstract}
  Large-scale rich behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study trends of human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian propabilistic model that can predict the hashtags used by the author of the post.
  Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
  so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of hundreds of millions of chunks occur in less than one second on a single processor.
  The model is a succesful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.

>>>>

\begin{abstract}
  Large-scale rich behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study trends of human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian probabilistic model that can predict the hashtags used by the author of the post.
  Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
  so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of hundreds of millions of chunks occur in less than one second on a single processor.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.
